On the Design of Complementary Filters for Control

### 2019-08-16 paper/paper.tex
Reworked the "three complementary filters" part

% Created 2019-08-16 ven. 22:07
% Intended LaTeX compiler: pdflatex
\documentclass[9pt, technote, a4paper]{ieeeconf}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[most]{tcolorbox}
\usepackage{siunitx}
\usepackage{amsmath,amssymb,amsfonts, cases}
\usepackage{algorithmic, graphicx, textcomp}
\usepackage{xcolor, import, hyperref}
\usepackage[USenglish, english]{babel}
\setcounter{footnote}{1}
\input{config.tex}
\author{\IEEEauthorblockN{Dehaeze Thomas\IEEEauthorrefmark{*}, Vermat Mohit and Collette Christophe} \\ \IEEEauthorblockA{Precision Mechatronics Laboratory, ULB\\ Brussels, Belgium\\ Email: \IEEEauthorrefmark{*}dehaeze.thomas@gmail.com}}
\date{2019-08-16}
\title{On the Design of Complementary Filters for Control}
\hypersetup{
 pdfauthor={\IEEEauthorblockN{Dehaeze Thomas\IEEEauthorrefmark{*}, Vermat Mohit and Collette Christophe} \\ \IEEEauthorblockA{Precision Mechatronics Laboratory, ULB\\ Brussels, Belgium\\ Email: \IEEEauthorrefmark{*}dehaeze.thomas@gmail.com}},
 pdftitle={On the Design of Complementary Filters for Control},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 26.2 (Org mode 9.2.5)},
 pdflang={English}}
\begin{document}

@@

\section{Introduction}
\label{sec:org1592c87}
  \label{sec:introduction}
The basic idea of a complementary filter involves taking two or more sensors, filtering out unreliable frequencies for each sensor and combining the filtered outputs to get a better estimate throughout the entire bandwidth of the system.
To achieve this, the sensors included in the filter should complement one another by performing better over specific parts of the system bandwidth.
A set of filters is said to be complementary if the sum of their transfer functions is equal to one at all frequencies, (i.e.) its magnitude is one and its phase is zero.

@@

\section{Requirements on the Design of Complementary Filters}
\label{sec:org045537e}
\label{sec:requirements}

\subsection{Sensor Fusion}
\label{sec:org68eba14}

@@

\subsection{Noise Sensor Filtering}
\label{sec:orgce86efa}

\subsection{Robustness of the Fusion}
\label{sec:orgc52988d}

\subsection{Upper bounds as a mathematical translation of the requirements}
\label{sec:org4ab877a}
\begin{quote}
The conclusion of the section should be that it is the norm of the complementary filter that is important and that is why we propose a method of synthesis based on H-infinity
\end{quote}

\section{Shaping of Complementary Filters using the \(\mathcal{H}_\infty\) Synthesis}
\label{sec:org4728e0e}
\label{sec:hinf_method}
First order complementary filters are easy to synthesize. For instance, one can use the following filters
\begin{equation}
H_H(s) = \frac{s/\w_0}{1 + s/\w_0}; \quad H_L(s) = \frac{1}{1 + s/\w_0}
\end{equation}
with \(\w_0\) is the tuning parameter corresponding to the crossover frequency of the filters.

However, the manual design of higher order complementary filters is far more complex and we have to use an automatic synthesis technique.

As shown in Sec. \ldots{}, most of the performance requirements can be expressed as upper bounds on the magnitude of the complementary filters.

@@

\subsection{\(\mathcal{H}_\infty\) problem formulation}
\label{sec:orgdd7b8f5}
   \label{sec:hinf_conf}
In this section, we formulate the \(\hinf\) problem for the synthesis of complementary filters.

@@

\subsection{Control requirements as \(\mathcal{H}_\infty\) norm of complementary filters}
\label{sec:org8724b71}
As presented in Sec. \ref{sec:trans_perf}, almost all the requirements can be specified with upper bounds on the complementary filters.
However, robust performance condition \eqref{eq:robust_perf_a} is not.

With the \(\mathcal{H}_\infty\) synthesis the condition \eqref{eq:hinf_problem} only ensure
\begin{align*}
  \hnorm{\begin{matrix} H_H w_H \\ H_L w_L \end{matrix}} \le 1 &\Leftrightarrow \max_\omega \sqrt{|w_L H_L|^2 + |w_H H_H|^2} \le 1\\
                                                             &\Rightarrow |w_L H_L| + |w_H H_H| \le \sqrt{2} \quad \forall\omega
\end{align*}

And thus we have almost robust stability.

\subsection{Choice of the weighting functions}
\label{sec:org04e66eb}
   \label{sec:hinf_weighting_func}
We here give some advice on the choice of the weighting functions used for the synthesis of the complementary filters.

The shape should be such that the performance requirements are met as explain in Sec. \ref{sec:trans_perf}.

@@

One should not forget the fundamental limitations of feedback control such that \(S + T = 1\).
Similarly, we here have that \(H_L + H_H = 1\) which implies that \(H_L\) and \(H_H\) cannot be made small at the same time.

\begin{equation}
  W(s) = G_c * \left(\frac{\frac{1}{\omega_0}\sqrt{\frac{1 - \left(\frac{G_0}{G_c}\right)^{\frac{2}{n}}}{1 - \left(\frac{G_c}{G_\infty}\right)^{\frac{2}{n}}}} s + \left(\frac{G_0}{G_c}\right)^{\frac{1}{n}}}{\frac{1}{\omega_0} \sqrt{\frac{1 - \left(\frac{G_0}{G_c}\right)^{\frac{2}{n}}}{\left(\frac{G_\infty}{G_c}\right)^{\frac{2}{n}} - 1}} s + 1}\right)^n
\end{equation}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/weight_formula.pdf}
\caption{\label{fig:weight_formula}
Amplitude of the proposed formula for the weighting functions}
\end{figure}

\subsection{Example}
\label{sec:orgf8bbd7b}

@@

@@

\subsection{Synthesis of Three Complementary Filters}
\label{sec:org916d6f2}

@@

\section{Application to the design of}
\label{sec:org7e3fe3e}
\label{sec:application}

\subsection{Specifications}
\label{sec:org7f6a128}

@@

\subsection{Weighting functions design}
\label{sec:orgdd7b46d}

@@

\subsection{Comparison}
\label{sec:orge13017e}

@@

\section{Conclusion}
\label{sec:org7a21636}
\label{sec:conclusion}

\section{Acknowledgment}
\label{sec:org56fbb7d}

>>>>

% Created 2019-08-16 ven. 23:34
% Intended LaTeX compiler: pdflatex
\documentclass[9pt, technote, a4paper]{ieeeconf}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[most]{tcolorbox}
\usepackage{siunitx}
\usepackage{amsmath,amssymb,amsfonts, cases}
\usepackage{algorithmic, graphicx, textcomp}
\usepackage{xcolor, import, hyperref}
\usepackage[USenglish, english]{babel}
\setcounter{footnote}{1}
\input{config.tex}
\author{\IEEEauthorblockN{Dehaeze Thomas\IEEEauthorrefmark{*}, Vermat Mohit and Collette Christophe} \\ \IEEEauthorblockA{Precision Mechatronics Laboratory, ULB\\ Brussels, Belgium\\ Email: \IEEEauthorrefmark{*}dehaeze.thomas@gmail.com}}
\date{2019-08-16}
\title{On the Design of Complementary Filters for Control}
\hypersetup{
 pdfauthor={\IEEEauthorblockN{Dehaeze Thomas\IEEEauthorrefmark{*}, Vermat Mohit and Collette Christophe} \\ \IEEEauthorblockA{Precision Mechatronics Laboratory, ULB\\ Brussels, Belgium\\ Email: \IEEEauthorrefmark{*}dehaeze.thomas@gmail.com}},
 pdftitle={On the Design of Complementary Filters for Control},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 26.2 (Org mode 9.2.5)},
 pdflang={English}}
\begin{document}

@@

\section{Introduction}
\label{sec:org1a92e6d}
  \label{sec:introduction}
The basic idea of a complementary filter involves taking two or more sensors, filtering out unreliable frequencies for each sensor and combining the filtered outputs to get a better estimate throughout the entire bandwidth of the system.
To achieve this, the sensors included in the filter should complement one another by performing better over specific parts of the system bandwidth.
A set of filters is said to be complementary if the sum of their transfer functions is equal to one at all frequencies, (i.e.) its magnitude is one and its phase is zero.

@@

\section{Requirements on the Design of Complementary Filters}
\label{sec:org8c17952}
\label{sec:requirements}

\subsection{Sensor Fusion}
\label{sec:org77e3eba}
\label{sec:sensor_fusion}

@@

\subsection{Noise Sensor Filtering}
\label{sec:org61f1e42}
\label{sec:noise_filtering}

\subsection{Robustness of the Fusion}
\label{sec:org88c9440}
\label{sec:fusion_robustness}

\subsection{Upper bounds as a mathematical translation of the requirements}
\label{sec:org2e8321f}
\label{sec:requirements_upper_bounds}

\textbf{The conclusion of the section should be that it is the norm of the complementary filter that is important and that is why we propose a method of synthesis based on H-infinity}

\section{Shaping of Complementary Filters using the \(\mathcal{H}_\infty\) Synthesis}
\label{sec:orgd9ea119}
\label{sec:hinf_method}
As shown in Sec. \ldots{}, most of the performance requirements can be expressed as upper bounds on the magnitude of the complementary filters.
As presented in Sec. \ref{sec:trans_perf}, almost all the requirements can be specified with upper bounds on the complementary filters.

@@

\subsection{\(\mathcal{H}_\infty\) problem formulation}
\label{sec:orgecc21d9}
\label{sec:hinf_synthesis}

In this section, we formulate the \(\hinf\) problem for the synthesis of complementary filters.

@@

\subsection{Choice of the weighting functions}
\label{sec:org6167188}
\label{sec:hinf_weighting_func}

We here give some advice on the design of the weighting functions used for the synthesis of the complementary filters using the \(\mathcal{H}_\infty\) method.

The weighting functions should be such that the performance requirements are met as explain in Sec. \ref{sec:trans_perf}.

@@

Moreover, the order of the complementary filters will be equal to the sum of the order of the weighting functions used.

One should not forget the fundamental limitations imposed by the synthesis: \(H_L(s) + H_H(s) = 1\).
This implies that \(H_L\) and \(H_H\) cannot be made small at the same time.

We here propose a formula for the design of the weighting function \eqref{eq:weight_formula}.

\begin{equation}
\label{eq:weight_formula}
  W(s) = \left(\frac{
           \hfill \frac{1}{\omega_0} \sqrt{\frac{1 - \left(\frac{G_0}{G_c}\right)^{\frac{2}{n}}}{1 - \left(\frac{G_c}{G_\infty}\right)^{\frac{2}{n}}}} s + \left(\frac{G_0}{G_c}\right)^{\frac{1}{n}}
         }{
           \left(\frac{1}{G_\infty}\right)^{\frac{1}{n}} \frac{1}{\omega_0} \sqrt{\frac{1 - \left(\frac{G_0}{G_c}\right)^{\frac{2}{n}}}{1 - \left(\frac{G_c}{G_\infty}\right)^{\frac{2}{n}}}} s + \left(\frac{1}{G_c}\right)^{\frac{1}{n}}
         }}\right)^n
\end{equation}
with:
\begin{itemize}
\item \(G_0\) is the absolute gain at low frequency
\item \(G_\infty\) is the absolute gain at high frequency
\item \(\omega_0\) and \(G_c\) define the absolute value of the filter at \(\omega = \omega_0\): \(|W(j\omega_0)| = G_c\)
\item \(n\) is the absolute slope of the filter, it is also equal to the order of the filter
\end{itemize}

The constrains are that \(G_0 < 1 < G_\infty\) and \(G_0 < G_c < G_\infty\) or that \(G_\infty < 1 < G_0\) and \(G_\infty < G_c < G_0\).

The shape of the weight generated using the formula is shown on figure \ref{fig:weight_formula}.

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/weight_formula.pdf}
\caption{\label{fig:weight_formula}
Amplitude of the proposed formula for the weighting functions, \(G_0 = 1e^{-3}\), \(G_\infty = 10\), \(\omega_c = \SI{10}{Hz}\), \(G_c = 2\), \(n = 3\)}
\end{figure}

\subsection{Example}
\label{sec:orgb30ba62}
\label{sec:hinf_example}

We are now using the proposed \(\mathcal{H}_\infty\) complementary filters synthesis method for a simple example.

The goal is to design

We use the formula \eqref{eq:weight_formula} for both \(w_L(s)\) and \(w_H(s)\).
The parameters used are summarized on table \ref{tab:weights_params}. And the magnitude of the weighting functions are shown on figure \ref{fig:weights_wl_wh}.

\begin{table}[!htpb]
\caption{\label{tab:weights_params}
Parameters used for the weighting functions}
\centering
\begin{tabular}{|l|X|X|}
\hline
Parameters & \(w_L\) & \(w_H\)\\
\hline
\(G_0\) & \(0.1\) & \(1000\)\\
\hline
\(G_\infty\) & \(1000\) & \(0.1\)\\
\hline
\(\omega_c\) [\(\si{Hz}\)] & \(11\) & \(10\)\\
\hline
\(G_c\) & \(2\) & \(2\)\\
\hline
\(n\) & \(2\) & \(3\)\\
\hline
\end{tabular}
\end{table}

@@

After synthesis, the obtain filters are:
\begin{align}
  H_L(s) &= \frac{10^{-8} (s+6.6e^9) (s+3450)^2 (s^2 + 49s + 895)}{(s+6.6e^4) (s^2 + 106 s + 3000) (s^2 + 72s + 3580)}\\
  H_H(s) &= \frac{(s+6.6e^4) (s+160) (s+4)^3}{(s+6.6e^4) (s^2 + 106 s + 3000) (s^2 + 72s + 3580)}
\end{align}

Their bode plot is shown on figure \ref{fig:hinf_synthesis_results}.

@@

\subsection{Synthesis of Three Complementary Filters}
\label{sec:org415d7ce}
\label{sec:hinf_three_comp_filters}

We want:
\begin{align*}
  & |H_1 w_1| < 1, \quad \forall\omega\\
  & |H_2 w_2| < 1, \quad \forall\omega\\
  & |H_3 w_3| < 1, \quad \forall\omega\\
  & H_1 + H_2 + H_3 = 1
\end{align*}

The \(\mathcal{H}_\infty\) objective is:
\begin{align*}
  & |H_1 w_1| < 1, \quad \forall\omega\\
  & |H_2 w_2| < 1, \quad \forall\omega\\
  & |(1 - H_1 - H_2) w_3| < 1, \quad \forall\omega\\
\end{align*}

And thus if we choose \(H_3 = 1 - H_1 - H_2\) we have solved the problem.

@@

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/hinf_three_synthesis_results.pdf}
\caption{\label{fig:hinf_three_synthesis_results}
Figure caption}
\end{figure}

\section{Application to the design of}
\label{sec:org57876bd}
\label{sec:application_ligo}

\subsection{Specifications}
\label{sec:orgc79cee4}
\label{sec:ligo_specifications}

@@

\subsection{Weighting functions design}
\label{sec:org6e51da2}
\label{sec:ligo_weights}

@@

\subsection{Comparison}
\label{sec:org06ff1a1}
\label{sec:ligo_results}

@@

\section{Conclusion}
\label{sec:orga86d375}
\label{sec:conclusion}

\section{Acknowledgment}
\label{sec:org8d338b6}
